---
title: "AIP-Group-Assignment"
author: "Group 35"
output: 
  html_document:
    toc: yes
    toc_depth: 3
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggpubr)
library(FSelector)
library(e1071) #SVM
library(scales)
library(caTools)
library(randomForest)
library(ROSE)
library(MASS)
library(caret)
library(pROC)
library(VGAM) #tobit
library(Hmisc)
library(corrplot)
options(warn = -1)
```

## Variable dictionary
Attributes | Description
--|---------
  1) Customer_ID| customer identification number
  2) recency| months since last purchase before the marketing campaign
  3) purchase_segment| categorisation for the purchase amount (£) in the past year before the marketing campaign
  4) purchase| actual purchase in the past year before the marketing campaign
  5) mens| whether the customer purchased men's merchandise in the past year before the marketing campaign (1 = yes)
  6) womens| whether the customer purchased women's merchandise in the past year before the marketing campaign (1 = yes)
  7) zip_area| categorisation of zip code as Urban, Suburban, or Rural
  8) new_customer| whether the customer is new in the past year or s/he is an existing customer (1 = yes)
  9) channel| the channels the customer purchased from in the past year. The categories are Phone, Web and Multichannel 
  10) email_segment| e-mail campaign the customer received, either for men's products or for women's products
  11) age| age of the customer in years
  12) dependent| whether the customer has a dependent or not (1 = yes)
  13) account| whether the customer has an account or not (1 = yes)
  14) employed| whether the customer has a permanant job (1 = yes)
  15) phone| whether the customer registered his/her phone or not (1 = yes)
  16) delivery| categorisation for the delivery address (1 = home; 2 = work; 3 = multiple)
  17) marriage| marital status (1=married, 2=single, 0 = others)
  18) payment_card| whether the customer registered a credit card for payment in the past year (1 = yes; 0 = no)
  19) spend| total amount spent in the following two weeks period
  20) visit| whether the customer visited the shop in the following two weeks period (1 = yes)

  
## Read the data
Set Customer_ID as character variable; recency, purchase and spend as numeric variables; and other attributes as factor variables.
```{r,warning=FALSE,message=FALSE}
visit_data <- read.csv("/Users/wenke/Desktop/AIP Assignment Files/assignment_data.csv",stringsAsFactors = TRUE)
str(visit_data)
visit_data[,1] <- as.character(visit_data[,1])#int to character
visit_data[,c(5,6,8,12:18,20)] <- lapply(visit_data[,c(5,6,8,12:18,20)],as.factor)#int to factor
str(visit_data) #to check the structure of the data
summary(visit_data) #to summarise the statistics of the data
```


## Data cleaning
Since the features "account" (all customers have account == 1) and "Customer_ID" are redundant and does not affect customer's visit, we choose to remove them. "purchase_segment" contains duplicated information as "purchase", so we remove these two variables as well.
```{r,warning=FALSE,message=FALSE}
visit_data$account <- NULL
visit_data$Customer_ID <- NULL
visit_data$purchase_segment <- NULL
```

Considering the substantial amount of observations, we choose to delete the NA of spend. 
```{r,warning=FALSE,message=FALSE}
visit_data <- filter(visit_data, !is.na(spend))
```

## Exploratory analysis
### Information Gain By Visit AND Spend
Information gain measures the reduction in entropy by splitting a dataset according to a given value of a random variable. As shown in Figure 1, variables “marriage”, employed” and “dependent” have the lowest information gain both for “visit” and “spend”, which thus would be removed for model simplicity. In addition, variable “age” contains zero IG for "visit”, which will also be eliminated in modelling part.
```{r,warning=FALSE,message=FALSE,fig.align="center"}
#calculate the visit weights
Visit_weights <- information.gain(visit~.,
                                  subset(visit_data,select = -c(spend,email_segment))) %>%
  arrange(desc(attr_importance)) %>%
  filter(attr_importance>0)
Visit_weights$attr_visit <- rownames(Visit_weights)
Visit_weights
#calculate the spend weights
Spend_weights <- information.gain(spend~.,
                                  subset(visit_data,select = -c(visit,email_segment))) %>%
  arrange(desc(attr_importance)) %>%
  filter(attr_importance>0)
Spend_weights$attr_spend <- rownames(Spend_weights)
Spend_weights
#plot the weights
par(mfrow=c(1,2),mar=c(10,3,2,3))
barplot(Visit_weights$attr_importance, names =Visit_weights$attr_visit,las = 2,ylim = c(0, 0.06),
        main = "Information gain calculated by Visit",cex.main=1,cex.axis=0.7,cex.names=0.7)
barplot(Spend_weights$attr_importance, names =Spend_weights$attr_spend,las = 2,ylim = c(0, 0.06),
        main = "Information gain calculated by Spend",cex.main=1,cex.axis=0.7,cex.names=0.7)
```

### Relationship between customer attributes and visit response after E-mail marketing
Attributes: mens, womens, purchase, recency, zip_area, dilivery, channel, phone, new_customer, payment_card
Dependent variable: Visit

According to the overall grey shape of all graphs, the sample sizes and customer attributes of Mens E-Mail, Women E-Mail and No E-Mail groups are basically the same. **E-mails are randomly sent to customers** regardless of any attributes, 1/3 receive mens e-mail, 1/3 receive womens e-mail and 1/3 receive no e-mail.

But according to the color composition of each set of graphs, we know that:

- Who tend to visit after E-Mail marketing
  **1. People who have a smaller recency and purchase amount between 500-1000 are affected most by the e-mail**, where the visit ratio of Mens E-Mail and Women E-Mail is obviously higher than No E-mail.
  
  2. New customers who deliver to work place and purchase on web are affected more by the e-mail, where the visit ratio of Mens E-Mail and Women E-Mail is moderately higher than No E-mail.
  
  3. People who live in rural areas, registered phone but didn't register credit card are possibly affected more by the e-mail, where the visit ratio of Mens E-Mail and Women E-Mail is slightly higher than No E-mail.

- Difference between Mens E-Mail and Womens E-Mail
  **2.1 customers who bought women's merchandise are more likely to visit after receiving the same gender e-mail**
  2.2 higher purchase customers are more responsive to mens email compared to womens email.

```{r,warning=FALSE,message=FALSE,fig.align="center"}
#mens and womens
ggarrange(
ggplot(visit_data,aes(x=womens))+geom_bar(stat="count")+
  facet_grid(email_segment~.)+scale_fill_brewer(palette = "Set2")+
  labs(x="Whether purchased women's merchandise", y = "Count of customers")+
  scale_fill_discrete(labels=c("No", "Yes")),
ggplot(visit_data,aes(x=mens))+geom_bar(stat="count")+
  facet_grid(email_segment~.)+scale_fill_brewer(palette = "Set2")+
  labs(x="Whether purchased men's merchandise", y = "")+
  scale_fill_discrete(labels=c("No", "Yes")),nrow=1)

ggarrange(
ggplot(visit_data,aes(x=factor(womens, levels= c("0","1"), labels = c("No", "Yes")),fill=visit))+geom_bar(stat="count",position = "fill")+
  facet_grid(email_segment~.)+
  labs(x="Whether purchased women's merchandise", y = "Percentage of customers")+
  scale_fill_brewer(palette = "Set2")+
  scale_fill_discrete(labels=c("No", "Yes")),
ggplot(visit_data,aes(x=factor(mens, levels= c("0","1"), labels = c("No", "Yes")),fill=visit))+geom_bar(stat="count",position = "fill")+
  facet_grid(email_segment~.)+
  labs(x="Whether purchased men's merchandise", y = "")
  +
  scale_fill_discrete(labels=c("No", "Yes")),nrow=1,common.legend=T)

#purchase and recency
ggarrange(
ggplot(visit_data,aes(x=purchase,))+
  geom_histogram(binwidth=10)+
  facet_grid(.~email_segment)+labs(x="The purchase amount (£) in the past year before the marketing campaign", y = "Count of customers")+xlim(0,1500)+ylim(0,750),
ggplot(visit_data,aes(x=recency))+
  geom_histogram(binwidth=1)+
  facet_grid(.~email_segment)+labs(x="Months since last purchase before the marketing campaign", y = "Count of customers")+xlim(0,13),nrow=2)

ggarrange(
ggplot(visit_data,aes(x=purchase,fill=visit))+
  geom_histogram(binwidth=10,position = "fill")+
  facet_grid(.~email_segment)+labs(x="The purchase amount (£) in the past year before the marketing campaign", y = "Percentage of customers")+xlim(0,1500)+scale_fill_brewer(palette = "Set2")+
  scale_fill_discrete(labels=c("No", "Yes")),
ggplot(visit_data,aes(x=recency,fill=visit))+
  geom_histogram(binwidth=1,position = "fill")+
  facet_grid(.~email_segment)+labs(x="Months since last purchase before the marketing campaign", y = "Percentage of customers")+xlim(1,13)+scale_fill_brewer(palette = "Set2")+
  scale_fill_discrete(labels=c("No", "Yes")),nrow=2)

#channel, zip_area, new_customer
ggarrange(
ggplot(visit_data,aes(x=factor(delivery, levels= c("1", "2", "3"), labels = c("Home","Work", "Multiple"))))+
  geom_bar(stat="count")+facet_grid(email_segment~.)+
  labs(x="The delivery address", y = "Count of customers"),
ggplot(visit_data,aes(x=factor(channel, levels= c("Multichannel", "Phone", "Web"), labels = c("Multi","Phone", "Web"))))+
  geom_bar(stat="count")+facet_grid(email_segment~.)+
  labs(x="The purchasing channel", y = ""),
ggplot(visit_data,aes(x=factor(new_customer, levels= c("0","1"), labels = c("No", "Yes"))))+
  geom_bar(stat="count")+facet_grid(email_segment~.)+
  labs(x="New customer", y = ""),
nrow=1,common.legend=T)

ggarrange(
ggplot(visit_data,aes(x=factor(delivery, levels= c("1", "2", "3"), labels = c("Home","Work", "Multiple")),fill=visit))+
  geom_bar(stat="count",position = "fill")+facet_grid(email_segment~.)+
  labs(x="The delivery address", y = "Percentage of customers")+scale_fill_brewer(palette = "Set2")+
  scale_fill_discrete(labels=c("No", "Yes")),
ggplot(visit_data,aes(x=factor(channel, levels= c("Multichannel", "Phone", "Web"), labels = c("Multi","Phone", "Web")),fill=visit))+
  geom_bar(stat="count",position = "fill")+facet_grid(email_segment~.)+
  labs(x="The purchasing channel", y = "")+scale_fill_brewer(palette = "Set2")+
  scale_fill_discrete(labels=c("No", "Yes")),
ggplot(visit_data,aes(x=factor(zip_area, levels= c("Rural", "Surburban", "Urban"), labels = c("Rural","Surburb", "Urban")),fill=visit))+
  geom_bar(stat="count",position = "fill")+facet_grid(email_segment~.)+
  labs(x="The zip code area", y = "Percentage of customers")+scale_fill_brewer(palette = "Set2")+
  scale_fill_discrete(labels=c("No", "Yes")),
nrow=1,common.legend=T)


#zip_area, phone, payment_card
ggarrange(ggplot(visit_data,aes(x=factor(zip_area, levels= c("Rural", "Surburban", "Urban"), labels = c("Rural","Surburb", "Urban"))))+
  geom_bar(stat="count")+facet_grid(email_segment~.)+
  labs(x="The zip code area", y = ""),
ggplot(visit_data,aes(x=factor(phone, levels= c("0","1"), labels = c("No", "Yes"))))+
  geom_bar(stat="count")+facet_grid(email_segment~.)+
  labs(x="Phone registered", y = ""),
ggplot(visit_data,aes(x=factor(payment_card, levels= c("0","1"), labels = c("No", "Yes"))))+
  geom_bar(stat="count")+facet_grid(email_segment~.)+
  labs(x="Credit card registered", y = ""),
nrow=1,common.legend=T)

ggarrange(
ggplot(visit_data,aes(x=factor(new_customer, levels= c("0","1"), labels = c("No", "Yes")),fill=visit))+
  geom_bar(stat="count",position = "fill")+facet_grid(email_segment~.)+
  labs(x="New customer", y = "")+scale_fill_brewer(palette = "Set2")+
  scale_fill_discrete(labels=c("No", "Yes")),
ggplot(visit_data,aes(x=factor(phone, levels= c("0","1"), labels = c("Not registered", "Registered")),fill=visit))+
  geom_bar(stat="count",position = "fill")+facet_grid(email_segment~.)+
  labs(x="Phone registered", y = "")+scale_fill_brewer(palette = "Set2")+
  scale_fill_discrete(labels=c("No", "Yes")),
ggplot(visit_data,aes(x=factor(payment_card, levels= c("0","1"), labels = c("Not registered", "Registered")),fill=visit))+
  geom_bar(stat="count",position = "fill")+facet_grid(email_segment~.)+
  labs(x="Credit card registered", y = "")+scale_fill_brewer(palette = "Set2")+
  scale_fill_discrete(labels=c("No", "Yes")),
nrow=1,common.legend=T)

```

  
## Modelling step 1: four visit prediction models - decide who we send email to
According to the evaluation results, Random Forest model with 6 attributes are most recommended.

### Data preparation
```{r}
#data selection
modeldata <- visit_data %>% filter(email_segment!="No E-Mail") %>% 
  subset(select = -c(employed,marriage,dependent))
#data partitioning
set.seed(123) 
partition = sample.split(modeldata$visit, SplitRatio = 0.7) 
training_set = subset(modeldata, select = -c(spend,age,email_segment), partition == TRUE) 
test_set = subset(modeldata, select = -c(spend,age,email_segment), partition == FALSE)
#data balancing
training_set <- ovun.sample(visit ~ ., data = training_set, method = "both", seed=1)$data
```


### Build 12 models
```{r,warning=FALSE,message=FALSE,fig.align="center"}
#Random Forest
rf_1 <- randomForest(visit ~ recency+purchase+channel, training_set)
rf_2 <- randomForest(visit ~ recency+purchase+channel+delivery+womens+new_customer, training_set,importance = T)
rf_3 <- randomForest(visit ~ ., training_set)
#Support Vector Machines
svm_1 <- svm(visit ~ recency+purchase+channel, training_set, kernel = "radial", scale = TRUE,probability = TRUE)
svm_2 <- svm(visit ~ recency+purchase+channel+delivery+womens+new_customer, training_set, kernel = "radial", scale = TRUE,probability = TRUE)
svm_3 <- svm(visit ~ ., training_set, kernel = "radial", scale = TRUE,probability = TRUE)
#Logistic Regression
logistic_1 <- glm(visit ~ recency+purchase+channel, training_set, family = binomial(link = "logit"))
logistic_2 <- glm(visit ~ recency+purchase+channel+delivery+womens+new_customer, training_set, family = binomial(link = "logit"))
logistic_3 <- glm(visit ~ ., training_set, family = binomial(link = "logit"))
#Linear Discriminant Analysis 
lda_1 <- lda(visit~recency+purchase+channel, training_set)
lda_2 <- lda(visit~recency+purchase+channel+delivery+womens+new_customer, training_set)
lda_3 <- lda(visit~., training_set)
```

###prediction, accuracy and ROC
```{r}
#Prediction
results <- as.data.frame(subset(test_set,select=c(visit)))
results$rf_1 <- predict(rf_1,test_set)
results$rf_2 <- predict(rf_2,test_set)
results$rf_3 <- predict(rf_3,test_set)
results$svm_1 <- predict(svm_1,test_set)
results$svm_2 <- predict(svm_2,test_set)
results$svm_3 <- predict(svm_3,test_set)
results$logistic_1 <- ifelse(predict(logistic_1,test_set,type = "response")>0.5,1,0)
results$logistic_2 <- ifelse(predict(logistic_2,test_set,type = "response")>0.5,1,0)
results$logistic_3 <- ifelse(predict(logistic_3,test_set,type = "response")>0.5,1,0)
results$lda_1 <- predict(lda_1,test_set)$class
results$lda_2 <- predict(lda_2,test_set)$class
results$lda_3 <- predict(lda_3,test_set)$class

#Calculate accuracy
model_evaluation <- data.frame(model=colnames(results[,-1]),accuracy="",auc="",precision="",recall="",F1="")
for (n in 1:12){
  model_evaluation[n,"accuracy"] <- scales::percent(length(which(results[ ,"visit"]==results[ ,n+1]))/length(results$visit),0.01)
  TP <- length(filter(results,visit==1,results[,n+1]==1)$visit)
  TN <- length(filter(results,visit==0,results[,n+1]==0)$visit)
  FP <- length(filter(results,visit==0,results[,n+1]==1)$visit)
  FN <- length(filter(results,visit==1,results[,n+1]==0)$visit)
  model_evaluation[n,"precision"] <- scales::percent(TP/(TP+FP),0.01)
  model_evaluation[n,"recall"] <- scales::percent(TP/(TP+FN),0.01)
  model_evaluation[n,"F1"] <- scales::percent(2*TP/(2*TP+FP+FN),0.01)
  }

#Prediction probabilities
results_prob <- as.data.frame(subset(test_set,select=c(visit)))
results_prob$rf_1 <- predict(rf_1,test_set,type = "prob")[,"1"]
results_prob$rf_2 <- predict(rf_2,test_set,type = "prob")[,"1"]
results_prob$rf_3 <- predict(rf_3,test_set,type = "prob")[,"1"]
results_prob$svm_1 <- attr(predict(svm_1,test_set,probability = T),"probabilities")[,"1"]
results_prob$svm_2 <- attr(predict(svm_2,test_set,probability = T),"probabilities")[,"1"]
results_prob$svm_3 <- attr(predict(svm_3,test_set,probability = T),"probabilities")[,"1"]
results_prob$logistic_1 <- predict(logistic_1,test_set,type = "response")
results_prob$logistic_2 <- predict(logistic_2,test_set,type = "response")
results_prob$logistic_3 <- predict(logistic_3,test_set,type = "response")
results_prob$lda_1 <- predict(lda_1,test_set)$posterior[,2]
results_prob$lda_2 <- predict(lda_2,test_set)$posterior[,2]
results_prob$lda_3 <- predict(lda_3,test_set)$posterior[,2]

#Calculate AUC
for (n in 1:12){
  model_evaluation[n,"auc"] <- round(auc(roc(results_prob$visit,results_prob[,n+1])),2)}
model_evaluation

#Plot the ROC curve
for (n in 2:13){
  assign(c(paste0("ROC_",colnames(results_prob)))[n],roc(results_prob$visit,results_prob[,n]))
}

ggroc(list(ROC_rf_1,ROC_rf_2,ROC_rf_3,ROC_svm_1,ROC_svm_2,ROC_svm_3,ROC_logistic_1,ROC_logistic_2,ROC_logistic_3,ROC_lda_1,ROC_lda_2,ROC_lda_3), 
      legacy.axes=TRUE) + 
    xlab("FPR") + ylab("TPR") +
    geom_abline(intercept = 0, slope = 1, 
                color = "darkgrey", linetype = "dashed")

ggarrange(
  ggroc(list(three = ROC_rf_1,six = ROC_rf_2,ten = ROC_rf_3), 
      legacy.axes=TRUE) + 
    labs(x="FPR",y="TPR",subtitle = "Random Forest",color="Number of attributes")+
    geom_abline(intercept = 0, slope = 1, 
                color = "darkgrey", linetype = "dashed"),
  ggroc(list(three = ROC_svm_1,six = ROC_svm_2,ten = ROC_svm_3), 
      legacy.axes=TRUE) + 
    labs(x="FPR",y="TPR",subtitle = "SVM",color="Number of attributes")+
    geom_abline(intercept = 0, slope = 1, 
                color = "darkgrey", linetype = "dashed"),
  ggroc(list(three = ROC_logistic_1,six = ROC_logistic_2,ten = ROC_logistic_3), 
      legacy.axes=TRUE) + 
    labs(x="FPR",y="TPR",subtitle = "Logistic Regression",color="Number of attributes")+
    geom_abline(intercept = 0, slope = 1, 
                color = "darkgrey", linetype = "dashed"),
  ggroc(list(three = ROC_lda_1,six = ROC_lda_2,ten = ROC_lda_3), 
      legacy.axes=TRUE) + 
    labs(x="FPR",y="TPR",subtitle = "LDA",color="Number of attributes")+
    geom_abline(intercept = 0, slope = 1, 
                color = "darkgrey", linetype = "dashed"),common.legend = T)

#PLot the importance plot of rf_2 model
varImpPlot(rf_2,main = "Variable importance as measured by the model suggested")
```
  
## Modelling step 2: decide the kind of email we send - women or men
different response of customers between women email marketing and men email marketing is only found among different merchandise group.
Those only purchased women merchandises are more likely to response to women email, those only purchased men merchandises or both men and women merchandises are more likely to response to men email.

```{r,warning=FALSE,message=FALSE,fig.align="center"}
filter(visit_data, email_segment!='No E-Mail',mens!=0|womens!=0) %>%
  group_by(mens,womens,email_segment) %>%
  summarise(total=length(visit),visit_number=sum(visit==1),responce_rate=visit_number/total) %>%
  mutate(category = ifelse(mens==0,"Womens only",ifelse(womens==0,"Mens only","Mens and Womens"))) %>%
  ggplot(aes(x=category,y=responce_rate,fill=email_segment))+geom_bar(stat = "identity",position = "dodge")+labs(x="Merchandises purchased in the past year", y = " Visit rate after recieving E-mail")

```

## Modelling step 3: estimate the spend increase

```{r,warning=FALSE,message=FALSE,fig.align="center"}
# predict the spend of customers once they visit
# no matter whether customer receive email or not, their "spend after visit" would adhere to the same Tobit model.
# vglm(spend~., tobit(Lower = 0, Upper = Inf), data = visit_data %>% filter(visit==1) %>% 
#        subset(select = -c(visit))) %>% summary()
tobit <- vglm(spend~., tobit(Lower = 0, Upper = Inf), data = visit_data %>% filter(visit==1) %>% 
  subset(select = -c(visit,email_segment,employed,marriage,dependent)))
summary(tobit)


email_number <- length(filter(visit_data,email_segment!="No E-Mail")$email_segment)

####calculate the spend increase if we apply the decision model to all customers

# apply models to whole dataset
visit_data2 <- visit_data
visit_data2$tobit_predicted_spend <- predict(tobit,visit_data2)
visit_prob <- as.data.frame(subset(visit_data2,select=c(tobit_predicted_spend)))
visit_prob$rf_1 <- predict(rf_1,visit_data,type = "prob")[,"1"]
visit_prob$rf_2 <- predict(rf_2,visit_data,type = "prob")[,"1"]
visit_prob$rf_3 <- predict(rf_3,visit_data,type = "prob")[,"1"]
visit_prob$svm_1 <- attr(predict(svm_1,visit_data,probability = T),"probabilities")[,"1"]
visit_prob$svm_2 <- attr(predict(svm_2,visit_data,probability = T),"probabilities")[,"1"]
visit_prob$svm_3 <- attr(predict(svm_3,visit_data,probability = T),"probabilities")[,"1"]
visit_prob$logistic_1 <- predict(logistic_1,visit_data,type = "response")
visit_prob$logistic_2 <- predict(logistic_2,visit_data,type = "response")
visit_prob$logistic_3 <- predict(logistic_3,visit_data,type = "response")
visit_prob$lda_1 <- predict(lda_1,visit_data)$posterior[,2]
visit_prob$lda_2 <- predict(lda_2,visit_data)$posterior[,2]
visit_prob$lda_3 <- predict(lda_3,visit_data)$posterior[,2]




#Predict average spend of marketing with different models, controlling the threshold to send the same amount of email as random marketing, email_number = 42732
spend_increase <- data.frame(model=colnames(results[,-1]),sum_spend="",random_spend="",threshold_p="")
for (n in 2:13){
visit_prob <- arrange(visit_prob,desc(visit_prob[,n]))
customer_selection <- visit_prob[1:email_number,]
spend_increase$sum_spend[n-1] <-sum(customer_selection$tobit_predicted_spend*
                                  customer_selection[,n])
spend_increase$random_spend[n-1] <- mean(replicate(1000,
                                     sum(sample(visit_prob$tobit_predicted_spend,size=email_number))*
                                     visit_prob[,n]/email_number))
spend_increase$threshold_p[n-1] <- customer_selection[email_number,n]
}
spend_increase$threshold_p <- as.numeric(spend_increase$threshold_p)
spend_increase$sum_spend <- as.numeric(spend_increase$sum_spend)
spend_increase$random_spend <- as.numeric(spend_increase$random_spend)

spend_increase <- mutate(spend_increase,average_spend=sum_spend/email_number)
spend_increase <- mutate(spend_increase,real_spend=sum(visit_data$spend)/email_number)
spend_increase <- mutate(spend_increase,increase1=average_spend-random_spend)
spend_increase <- mutate(spend_increase,increase2=average_spend-real_spend)
spend_increase

```

```{r}
#Predicted average spend of marketing using the best model with different thresholds
prediction_spend <- data.frame(threshold_p="",email_percentage="",sum_spend="",average_spend="")
i = 0
for (p in seq(0.01,0.99,0.01)){
  i = i+1
  prediction_spend[i,1] <- p
  customer_selection <- filter(visit_prob,visit_prob$rf_2>p)
  prediction_spend[i,2] <- length(customer_selection$rf_2)/length(visit_prob$rf_2)
  sum_spend <- sum(customer_selection$rf_2*customer_selection$tobit_predicted_spend)
  average_spend <- sum(customer_selection$rf_2*customer_selection$tobit_predicted_spend)/
                       length(customer_selection$tobit_predicted_spend)
  prediction_spend[i,3] <- ifelse(sum_spend>0,sum_spend,NA)
  
  prediction_spend[i,4] <- ifelse(sum_spend>0,average_spend,NA)}
prediction_spend

#Plot average spend of marketing with different models and different thresholds
prediction_spend$threshold_p <- as.numeric(prediction_spend$threshold_p)
prediction_spend$sum_spend <- as.numeric(prediction_spend$sum_spend)
prediction_spend$average_spend <- as.numeric(prediction_spend$average_spend)
prediction_spend$email_percentage <- as.numeric(prediction_spend$email_percentage)

ggarrange(
ggplot(prediction_spend,aes(x=threshold_p,y=sum_spend))+geom_line()+
  geom_vline(xintercept = 0.92, linetype = "dashed")+
  geom_hline(yintercept = sum(visit_data$spend), linetype = "dashed")+
  labs(x="",y="Total spend")+
  annotate("text",x=0.3, y=1100000, label = 'Total spend of the last random marketing = 887502.2')+
  annotate("text",x=0.96, y=1500000, label = 'p = 0.92'),

ggplot(prediction_spend,aes(x=threshold_p,y=email_percentage))+geom_line()+
  geom_vline(xintercept = 0.92, linetype = "dashed")+
  geom_hline(yintercept = length(filter(visit_data,email_segment!="No E-Mail")$email_segment)/length(visit_data$email_segment), linetype = "dashed")+ 
  geom_hline(yintercept = 0.15, linetype = "dashed")+
  labs(x="",y="Received email")+
  annotate("text",x=0.2, y=0.25, label = 'Percentage = 15%')+
  annotate("text",x=0.5, y=0.8, label = '66.8% customers received E-mail in the last random marketing'),

ggplot(prediction_spend,aes(x=threshold_p,y=average_spend))+geom_line()+
  geom_vline(xintercept = 0.92, linetype = "dashed")+
  geom_hline(yintercept = mean(filter(visit_data,spend!=0)$spend),linetype = "dashed")+
  labs(x="Threshold probability",y="Average spend")+
  annotate("text",x=0.2, y=100, label = 'Mean of spend(>0) = 88.36'),
nrow = 3,common.legend =T,legend="right",align = "hv")
```









